%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4
\usepackage{amssymb}
\defaultfontfeatures{Path = /usr/local/texlive/2014basic/texmf-dist/tex/latex/fontawesome/}
\usepackage{fontawesome}

\begin{document}
\newcommand{\addmargin}{\vspace{2mm}}
\newcommand{\addmarginbetween}{\vspace{4mm}}
\newcommand{\lastmargin}{\vspace{0.5mm}}
\definecolor{black}{HTML}{000000} \definecolor{blue}{HTML}{4285F4}
\definecolor{red}{HTML}{EA4335}
\definecolor{green}{HTML}{34A853}
\definecolor{googleYellow}{HTML}{FBBC05}
\definecolor{uberColor}{HTML}{4F5354}
\renewcommand{\labelitemi}{\color{black}\scalebox{.5}{$\blacksquare$}}
\renewcommand{\baselinestretch}{1.2}

%------------------------------------------------
% TITLE SECTION
%------------------------------------------------

\namesection{Ayush}{Bhagat} { % Your name
  \faGlobe\hspace{3pt}\href{http://ayushbhagat.com}{ayushbhagat.com}\hspace{26pt}
  \faEnvelope\hspace{3pt}\href{mailto:ayushbhagat@gmail.com}{ayushbhagat@gmail.com}\hspace{26pt}
  \faGithub\hspace{3pt}\href{https://github.com/ayushbhagat}{ayushbhagat}\hspace{26pt}
  \faLinkedin\hspace{3pt}\href{https://ca.linkedin.com/in/ayushbhagat}{ayushbhagat}
}

\begin{minipage}[t]{\textwidth}

%------------------------------------------------
% Skills
%------------------------------------------------

\ssection{Skills}
\ssubsectionWithoutSpaceAtEnd{Languages}{JavaScript, Java, C++, Python}
\hspace{25pt}\ssubsectionWithoutSpaceAtEnd{Other}{HTML, CSS, NPM, Webpack, Git, Vim, Tmux}\\
\ssubsectionWithoutSpaceAtEnd{Frontend}{React, Redux, jQuery, Android}
\hspace{28pt}\ssubsectionWithoutSpaceAtEnd{Backend}{Node.js, Express, PostgreSQL, MongoDB}\\
\sectionspace

%------------------------------------------------
% Experience
%------------------------------------------------
\ssection{Experience}

%------------------------------------------------

\jobSectionHeading{\color{uberColor}Uber}{Software Engineer, Intern}{Jan 2017 - Apr 2017 | Security}
\vspace{4.2mm}
\begin{tightitemize}
\item Independently created an accounts management \boldit{React} \href{http://accounts.uber.com/profile}{app} used by \boldit{thousands} to edit their profile. \\
\vspace{2pt}
Check it out here:\href{http://accounts.uber.com/profile}{\boldit{accounts.uber.com/profile}}.
\item Added Facebook Login to Uber's mobile website using \boldit{React} and \boldit{Express}.
\item Helped architect frontend projects owned by the team and performed code reviews.
\end{tightitemize}

\sectionspace
\addmarginbetween

%------------------------------------------------

\jobSectionHeading{\color{googleYellow}Snapchat}{Software Engineer, Intern}{May 2016 - Aug 2016 | Unlockables}
\vspace{4.2mm}
\begin{tightitemize}
\item Individually created the community geofilters submission \href{https://www.snapchat.com/geofilters/submit.html}{page}, a \boldit{React} app used by \boldit{thousands}. \\
\vspace{2pt}
Check it out here:\href{https://www.snapchat.com/geofilters/submit.html}{\boldit{snapchat.com/geofilters/submit.html}}.
\item Developed features using \boldit{ES6}, \boldit{React} and \boldit{Redux} for an internal tool used to manage unlockables.
\item Implemented backend functionality for frontend features using \boldit{Java} and \boldit{Google Endpoints API}.
\end{tightitemize}

\sectionspace
\addmarginbetween

%------------------------------------------------

\jobSectionHeading{\color{blue}G\color{red}o\color{googleYellow}o\color{blue}g\color{green}l\color{red}e}{Software Engineer, Intern}{Sep 2015 - Dec 2015 | Display Ads}
\vspace{2mm}
\color{black}
\fontspec[Path = fonts/lato/]{Lato-Lig}
\fontsize{9pt}{9pt}
\begin{tightitemize}
\item Developed for a high revenue, backend server-side system that serves \boldit{billions} of queries per day.
\item Redesigned a critical component in the ad-serving infrastructure to increase speed and performance.
\item Implemented my design in \boldit{C++11} and wrote unit tests with at least \boldit{80\%} code coverage.
\end{tightitemize}

\sectionspace
\addmarginbetween

%------------------------------------------------

\jobSectionHeading{\color{blue}G\color{red}o\color{googleYellow}o\color{blue}g\color{green}l\color{red}e}{Software Engineer, Intern}{Jan 2015 - Apr 2015 | Shopping Now}
\vspace{2mm}
\color{black}
\fontspec[Path = fonts/lato/]{Lato-Lig}
\fontsize{9pt}{9pt}
\begin{tightitemize}
\item Performed data analytics and visualizations on big data to monitor user activity for Google Shopping.
\item Created a \boldit{MapReduce} pipeline using \boldit{FlumeJava} to calculate aggregated statistics from \boldit{billions} of user data entries.
\item Wrote and optimized \boldit{Dremel} queries that extract statistics from various tables to power dashboards, which are used by several teams within Google Shopping.
\end{tightitemize}

\sectionspace
\vspace{-5mm}

%------------------------------------------------
% Projects
%------------------------------------------------

\ssection{Projects}
\ssubsection{\href{https://github.com/uwblueprint/somo-react}{Somo (UW Blueprint)}}{Web tool for a Kenyan non-profit to create and send surveys through SMS.}\\
\ssubsection{\href{https://github.com/DogWalkers/whiteboard}{Whiteboard (hackWaterloo)}}{Web app for developers to search and connect with other developers.}\\
\vspace{-10pt}

%------------------------------------------------
% Education
%------------------------------------------------

\ssection{Education}
\sssubsection{University of Waterloo}{\itit{Bachelor in Software Engineering (BSE)}Expected April, 2018}\\
\ssubsection{Awards}{Honours Dean's List All Terms\hspace{4pt}\itit{(89\% Average)}\hspace{-4pt}, President's Scholarship of Distinction}\\

\end{minipage} % The end of the first page

%------------------------------------------------
% SECOND PAGE (EXAMPLE)
%------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%------------------------------------------------

\end{document}
